Introductory Physics Labs: A Tale of Two Transformations

### 2020-08-27 manuscript/onlineLabPaper.tex
Draft is still long, but I have to give it a break.  I think that we should work to shorten my description of the ADI curriculum.  I've started an addendum, but only just started it.  It will need some significant work (as it is essentially just the previous revision of the paper dumped into a tex file.

\author{First Author} \affiliation{Masked Institution} \author{Second Author}
\affiliation{Masked Institution}

@@

% There is no abstract in a TPT paper.
%\begin{abstract}
%  A key problem facing physics departments, especially given the current global pandemic, is
%  how can we engage students in our laboratory courses while maintaining appropriate social
%  distancing and hygiene standards.  One solution to this problem is to move the labs to an
%  online format.  But how can we do this while \textit{also} engaging our students in online
%  labs with a curriculum that privileges science practices?  We have created an intro physics
%  lab curriculum that engages students in science practices and are implementing it online.
%\end{abstract}

@@

\section{Introduction}
 A key problem facing physics departments, especially given the current global pandemic, is
  how can we engage students in our laboratory courses while maintaining appropriate social
  distancing and hygiene standards.  One solution to this problem is to move the labs to an
  online format.  But how can we do this while \textit{also} engaging our students in online
  labs with a curriculum that privileges science practices?  We have created an intro physics
  lab curriculum that engages students in science practices and are implementing it online.

Scientific truth is discovered through the practice of doing science.  In fact, the National
Research Council in it's report on Discipline Based Education Research (DBER) states, ``Without
[scientific] investigative practices, there would be no new scientific and engineering
knowledge.''\cite{DBERreport} However, too often, laboratory courses do not meaningfully engage
students in scientific practices, instead reproducing classical experiments.\cite{PCAST12} This
is part of a long-standing tradition of calling for authentic engagement in scientific
practices which pre-dates Lorentz transformations.\cite{AAAS1881} Indeed, the AAAS stated our
goals quite succinctly, ``[Typical courses in t]he sciences\ldots are not made the means of
cultivating the observing powers, stimulating inquiry, exercising the judgment in weighing
evidence, nor of forming independent habits of thought.''\cite{AAAS1881}

The situation at our home institution in the Fall of 2016 very much mirrored the national
narrative.  The lab curriculum had been largely unchanged for about 20 years, and followed the
traditional cookbook lab paradigm.  Moreover, the equipment commonly used by students was
xxpart of an interdisciplinary team interested in engaging students in scientific practices as
well as assessing those scientific practices, we secured funding, both internally and from the
NSF, to change this status quo in physics, biology, and chemistry.  All three departments
transformed their labs using a pedagogical framework entitled, Argument Driven Inquiry
(ADI),\cite{Sampson2011,Walker2011,Walker2016} which has been specifically designed to engage
students in authentic science practices. We will focus on the physics transformation in this
paper.

We were satisfied with our progress when March 2020 rolled around, and with it, the mandatory
shut-down due to the global COVID-19 pandemic.  With students off campus, we had to abruptly shift our
delivery to an online format and quickly realized that some of the activities that we utilized
in the face-to-face sections had to be adapted to online use.  Going forward, we have further
adapted what we are doing so that students can still participate in a hands-on laboratory
experience in an online laboratory course.  We hope these changes will be meaningful long-term as a lack of online labs is
also a barrier for distance education students' completion of a degree.  So online lab curricula would fill an
institutional need.  In the next sections, we will discuss our institutional and instructional
contexts and describe each transformation in more detail.

\section{Instructional Context}
\textcolor{red}{This section needs to have the institution masked before we send it in.}

East Carolina University is a regional master's university in a rural, economically depressed
part of our state.  The university mission is focused on regional transformation and service to
this region.  The total student population in Fall 2019 was 29k.  Our physics labs (Physics 1
lab and Physics 2 lab) are each 1 credit courses that meet for 2 hours per week. These courses
serve both of our Calculus-based and Algebra-based physics lecture courses.  Most $(\sim 75\%)$
of the students who take our lab course are in (or have taken) the Algebra-based physics
lecture course. It also fulfills the general education requirement for science lab courses at
our university.  Table \ref{tab:gender} compares the gender of students in these lab courses
compared to the university population.  We note that the gender distribution of students in the
Physics 2 lab generally matches the university population, while the Physics 1 lab skews more
heavily male than the university population.  We also compare the race of students in these
contexts in Table \textcolor{red}{not ready yet}\ldots

Students who take these labs are most often science majors, especially in the health sciences
(e.g., Biology, Exercise Science), but this lab is also taken by our majors.  In Fall 2019 we
had 409 students in the Physics 1 lab, and in Spring 2020 (at Census Day, before the pandemic
changed enrollments) we had 256 students in the Physics 2 lab.  In both labs, our enrollment is
capped at 22 students, due to the constraints of our laboratory classroom.

Labs are supervised by MWS, but each section is run by Graduate GTAs (GTAs). The transformed
curriculum was jointly written by both of the authors.  GTA training was greatly enhanced when
the new lab curriculum was put in place.  SFW and MWS, along with colleagues in Biology and
Chemistry, run a training for all GTAs in Biology, Chemistry, Geology, and Physics as these
disciplines are all using the same curricular format for their labs.  MWS runs a weekly prep
meeting with the GTAs, and SFW and the research team have supervised various aspects of the
transformation especially important for research such as curricular implementation \cite{AL's
  paper} and assessment practices \cite{Wolf2019}.

\begin{table}
  \centering
  \begin{tabular}{l|ll|l}
    \hline \hline							
    &	\multicolumn{2}{c|}{Course}\\
    Gender	&	Physics 1	&	Physics 2	&	University	\\ \hline
    Female	&	41.8\%	&	60.9\%	&	57.1\%	\\
    Male	&	58.2\%	&	39.1\%	&	42.9\%	\\
    \hline \hline							
  \end{tabular}
  \caption{Gender breakdown of students in the Fall 2019 of the Physics 1 lab, the Spring 2020
    Physics 1 lab, and the undergraduate poplulation of the university at large in Fall 2019.
    Note: The university only collected binary gender data }
  \label{tab:gender}
\end{table}

\section{Transformation \#1: Argument Driven Inquiry}
Argument Driven Inquiry (ADI) is a pedagogical method that was developed to make science labs
in school better match what actually transpires in authentic research settings
\cite{Walker2011,Sampson2011,Walker2016}.  In traditional labs, we often ask students to answer
questions, or measure quantities, that are well-known using procedures that have been refined
over time.  For example, in physics we often have students measure $g$ using a well-known
method (such as a spark timer).  In ADI labs, we give students a question to answer (e.g.,
``Does the force a fan exerts on a cart depend on the mass of the cart?''), allow them to
design a procedure for an experiment that will answer that question, collect and analyze their
data, and make claims based on their data.  We accomplish this by having students engage in a
three-part cycle:
\begin{itemize}
  \item Pre-Lab - Introducing the context
  \item Proposal Development and Data Collection
  \item Argumentation and Peer Review
\end{itemize}
In the sections below, we will comment on each part of the cycle, focusing on both students and
GTAs.

\subsection{Session 1: Pre-Lab}
Part of the goal of any laboratory is to help students develop a familiarity with certain tools
and equipment common to the lab.  The purpose of the pre-lab reading and activity is to give
students familiarity with the equipment they will be using.  For the investigation 
described previously, ``Does the force a fan exerts on a cart depend on the mass of the cart?''
we need students to become familiar with a few things, such as what we mean by a cart, and give
them some tools that they need to be able to answer this question.  As a part of the pre-lab
reading, students are given information about linear regression---both how to run it in Excel, and
how to interpret the output, and how we can estimate instantaneous velocity given position
vs.\ time data. For this experiment, we give them a cart (leaving the fan off for now) and have
them measure the acceleration of that cart down a ramp using an ultrasonic motion detector to
collect position vs.\ time data for this motion.  Students work in pairs to do this work, and
turn in a brief summary of this work on the course management system.  For this investigation,
it is the first time that they create graphs, so we set norms for graphing such as helping them
decide which variable to put on the x-axis and the y-axis as well as including units.  Pre-lab
assignments are designed to be graded in less than 1 minute/paper based on a rubric we provide
to both students and GTAs.

\subsection{Session 2: Proposal Development and Data Collection}
During this session, students work in groups of 4 to develop a proposal, get it approved by a GTA,
and then collect and analyze their data.  We have a format for proposal development that asks
students to link the scientific concept being studied---in this example case, Newton's Second
Law---to the data that they will collect.  Students also need to propose a plan for analyzing
their data and minimizing potential sources of error (such as friction).  Once students have an
approved proposal, they begin collecting and analyzing their data.  This may lead them to
refine or revise their method (which they are encouraged to do).  Grading for the GTAs this
week is minimal (full credit for completing the proposal).  However, this is the most critical
week's for GTA training.  GTAs have to be clear that the goal is to allow a diverse number of
ways of collecting/analyzing this data.  How much does the mass of the cart need to vary?  How
many different cart masses do the students need to take?  How should students deal with
friction? All of these are questions that we want the \textit{students} to answer.  And in some
sense, we will be disappointed if all of the students come up with the same answer.
Experimental methods certainly have an impact on experimental results.

\subsection{Session 3: Argumentation and Peer Review}
During this session, the students begin by sharing their results.  Students finish analyzing their
data during the prior week, and prepare a ``poster'' on a whiteboard.  One person from the
group stays at the whiteboard while the other group members (travelers) go to other groups.
The travelers learn what other groups did, and compare to their results in a structured
argumentation setting.  Groups spend about 3--5 minutes at a poster, and rotate so that they see
at least 3 other posters.  After the travelers return, critically, the groups spend time
discussing what they saw and reflecting on their own results.  What is exciting is that
sometimes, these interactions actually drive groups to change their claims \cite{Walker2019}.

Each student writes a shortened lab report consisting of three sections: an introduction to the
scientific concept, a description of the experimental method or procedure, and a discussion
section laying out their results and the evidence and justification supporting their results. 
The authors have created different peer review calibration videos for the students to watch so
they can look for the same things that we are going to be grading them on when we get
their final reports.  Students complete their lab report and submit it by the end of the day.
Then, students take part in double-confidential peer review.  We facilitate this online.  They
read and reply to two different lab reports.  Finally, they get their feedback and use this to
revise their own lab report.  At the end of this week, students turn in their revised,
peer-reviewed final lab report.  This is the heaviest week of GTA grading.  We provide a rubric
for lab report grading, and each lab report generally takes about 3-5 minutes to grade.

@@

In March 2020 the COVID-19 pandemic forced most universities, including ours, to move all their classes online. Our General Physics I and II laboratories had
completed two out of four full investigations and the pre-lab for the third investigation
face-to-face. We were forced to find a way to engage students in an online format while
preserving the nature of the ADI laboratory experience. The face-to-face activities that we
moved online were the Investigation 3 Proposal and Argumentation and the Investigation 4
Pre-Lab, Proposal, and Argumentation. In addition, we gave our laboratory practical exam
online. We required student investigation groups to find a method for online collaboration in
which everyone in the group could participate. Some groups used Cisco WebEx (video interaction
platform licensed by our university) sessions, some used a group chat, and others used FaceTime
or other online communication applications.

During the first week of online classes each group produced their proposal and posted a proposal form on a Canvas
Discussion for approval. The GTA reviewed proposals and
provided feedback or approval. Groups used the GTA feedback to revise their proposals until they
were approved. Most proposals obtained approval after two or three revisions, but some required
as many as seven revisions to obtain approval. The GTAs and students found communication about
proposals much more difficult online than in face-to-face classes. When the GTA approved a group's proposal, they assigned the group a data set for the
investigation, and the group began its measurements and analysis. We provided measurements to
the students in the most raw form possible to require them to make decisions about data
collection and analysis.

Investigation 3 in the General Physics Laboratory I course was a study of the periodic motion
of a mass hanging from a spring in which the students were asked to determine when the spring's
mass must be considered as a contribution to the period. Before the transition to online
classes the students had completed a pre-lab activity in which they measured the period of a
mass on a spring. For this investigation we provided videos of various masses oscillating on
springs (100 oscillations each for 10 different masses and for the spring oscillating with no
mass) and photographs of each spring and each mass on a balance. We posted video and photograph
sets for six different springs so groups in the same lab section would each have different
springs to study.

Investigation 3 for the General Physics Laboratory II course was a study of light diffraction
in which the students were asked to determine whether hairs from two individuals had the same
diameter. Before the transition to online classes, the students had completed a pre-lab
activity in which they determined the width of a single slit by measuring the diffraction
pattern. We collected hair samples from several people and posted photographs of the
diffraction pattens of the hairs. Each photograph had a ruler at the bottom for the students to
use as a length scale. We also provided photographs of the positions of the holder and screen
on the optics bench. We gave the students a tutorial on using the \emph{ImageJ}
application\citep{schrasetal12} to measure distances in a photograph.

Each group was required to complete its analysis and create a
three-slide presentation for the argumentation session the following week. The first slide was
a description of their measurements. Te second slide was a presentation of the results,
including a graph or table, and the third slide was their argument, based on their result.

The argumentation session was held in a Cisco WebEx session during the lab session the week
after the proposal session. One member of each group gave the presentation, which was followed
by questions. Students received credit for giving presentations, asking meaningful questions,
and responding to questions.  Following the argumentation session students submitted individual
draft reports, peer-reviewed each other's drafts, and submitted final reports in the same
manner used for the face-to-face investigations.

Investigation 4 in the General Physics Laboratory I course was about collisions, and students
were asked to determine whether a collision between two marbles was elastic. Our original plans
were to have the students video marble collisions in lab and analyze them using the \emph{Tracker}
application\citep{bro2009}, which is installed on the computers in the laboratory. When the labs went online, we provided the students with several
videos of marble collisions and asked the students to install \emph{Tracker} on their computers for
analysis.  We adapted the Investigation 4 Pre-Lab assignment so students could perform them on
their own computers. The originally-planned pre-lab was an analysis of a video using
\emph{Tracker}. This activity required only a few changes from the face-to-face pre-lab assignment. We
conducted the proposal session as described for Investigation 3 and assigned each group one of
six videos of colliding marbles to analyze along with mass measurements of the marbles in the
videos. The argumentation session and the remainder of the investigation were conducted in the
same manner as Investigation 3.

Investigation 4 in the General Physics Laboratory II course was a study of radioactive
decay. The pre-lab for the face-to-face course is a simulation of radioactive decay using dice
in which the students roll several dice and remove all the dice with one dot showing. We wrote
a GlowScript\citep{glowscript} program to ``roll'' randomized virtual dice so they could
perform the same activity using this simulation on their computers. For the investigation the
students were asked to determine which isotope was most common in the nuclear decay of a copper
disk that had been exposed to low-energy neutron radiation. We measured radiation counts for
several disks and also background levels and provided students with \SI{30}{s} counts vs.\ time
in CSV files for analysis. As in the other course, the investigation was conducted in the same
manner as Investigation 3.

@@

We encountered many problems with the move to online laboratories. Our students had not
registered for an online class, and many were not prepared for the sudden transition from
face-to-face to online classes. Many students could not or did not attend the online WebEx
sessions or participate with their assigned groups. Some students had to get jobs when they
returned home, and many students did not have access to high-speed internet. We removed
non-participating students from groups and gave them an opportunity to make up their missed
work asynchronously. Less than \SI{50}{\percent} of the students in the make-up groups
completed their work. We resorted to dropping the lowest investigation for the course.

Some students in the course did not have access to computers capable of running \emph{Tracker} or
\emph{ImageJ}, both of which run on Windows, Macintosh, or Linux computers but not Chromebooks or
mobile devices such as smartphones or tablets. We discovered \emph{jsTrack}\citep{jstrack}, an online
Javascript web application for video analysis that runs on most computers including
Chromebooks. Students using mobile devices were not able to use \emph{jsTrack} either.

@@

\begin{table}
  \caption{\label{tab: 1251 fall} General Physics Laboratory I investigations for Fall 2020
    block schedule.}
  \begin{ruledtabular}
    \begin{tabular}{ccp{28em}}
      Investigation & Topic & Guiding Question\\
      \hline
      1 & 1-D kinematics & Does a ball rolling on an incline have the same acceleration on the way up as it does on the way down? \\
      2 & Periodic motion & At what nut position is the period of the physical pendulum equal to \SI{1.30}{s}? \\
      3 & 2-D collisions & Is the collision between two marbles elastic?
    \end{tabular}
  \end{ruledtabular}
\end{table}

We decided to hold our introductory physics laboratory courses online in the Fall 2020 semester
in order to preserve the group class interaction aspects of ADI, which would be difficult under
the social distancing requirements in place due to the pandemic.\citep{mclber20} Also our
teaching laboratories would have to operate at half-capacity face-to-face to maintain social distancing,
preventing us from offering the courses to the necessary number of students.  In addition to
the social distancing requirements for face-to-face class meetings, our university adopted an
eight-week block schedule, with the second block ending before the Thanksgiving holiday. Half
of the Fall 2020 courses were scheduled for the first eight-week block, and half of the courses
were scheduled for the second block. Course mapping between the originally scheduled 14-week
semester and the two eight-week blocks was based on the originally scheduled class meeting
time. In the block schedule, the one semester-hour lab courses have two two-hour meetings per
week. We determined that, even though there were enough lab meetings for the synchronous
activities of four full investigations, there was not enough time between lab meetings for the
asynchronous components and timely grading for four investigations. We reduced the number of
investigations to three and added an additional pre-lab activity to each investigation. The
topics for the three investigations and the guiding questions are in Table \ref{tab: 1251 fall}
for General Physics Laboratory I and in Table \ref{tab: 1261 fall} for General Physics
Laboratory II.

\begin{table}
  \caption{\label{tab: 1261 fall} General Physics Laboratory II investigations for Fall 2020
    block schedule.}
  \begin{ruledtabular}
    \begin{tabular}{ccp{26em}}
      Investigation & Topic & Guiding Question\\
      \hline
      1 & Current and resistance & Does a light bulb behave like a resistor? \\
      2 & Time varying circuits & Do two of the lab kit capacitors have the same capacitance? \\
      3 & Diffraction of light & Are hairs from different people the same diameter?
    \end{tabular}
  \end{ruledtabular}
\end{table}

We informed the students before the course began that internet connectivity was required and
that they must have access to a computer capable of running \emph{Tracker} (General Physics Laboratory
I) or \emph{ImageJ} (General Physics Laboratory II). We also included these statements in the course
syllabus. Although the courses were online, most of the students were on campus allowing them
to access campus computer laboratories if they did on a computer that met the course
requirements.

\begin{table}
  \caption{\label{tab: 1251 lab kit} General Physics Laboratory I lab kit contents.}
  \begin{tabular}{clc}
    \hline\hline
    Quantity & Item & Investigation(s)\\
    \hline
    1 & Protractor & 1 \\
    2 & \SI{25}{mm} marble & 1, 3 \\
    1 & Tape measure with cm scale & 1, 2, 3\\
    1 & \SI{0.6}{m} threded rod & 2 \\
    1 & Eye nut & 2 \\
    3 & Nuts & 2 \\
    1 & Door hook & 2 \\
    1 & \SI{1}{m} string & 2 \\
    1 & \SI{16}{mm} marble & 3 \\
    \hline\hline
  \end{tabular}
\end{table}

We developed lab kits with supplies that allowed the students to perform the investigations
outside the teaching laboratory. We purchased the lab kit items in collaboration with our
campus bookstore, and the students purchased the lab kits from the bookstore. We ordered lab
kit items in bulk and where possible directly from manufacturers to reduce the costs of the
items. Each General Physics Laboratory I kit cost ???, and each General Physics Laboratory II
kit cost \$39.00. Table \ref{tab: 1251 lab kit} shows the lab kit contents for General Physics
Laboratory I, and Table \ref{tab: 1261 lab kit} shows the lab kit contents for General Physics
Laboratory II.

\begin{table}
  \caption{\label{tab: 1261 lab kit} General Physics Laboratory II lab kit contents.}
  \begin{tabular}{clc}
    \hline\hline
    Quantity & Item & Investigation(s)\\
    \hline
    1 & \SI{100}{\ohm} resistor & 1 \\
    1 & \SI{330}{\ohm} resistor & 1 \\
    1 &  \SI{100}{\ohm} potentiometer & 1 \\
    1 & E10 light bulb holder & 1 \\
    1 & \SI{5}{V} E10 incandescent light bulb & 1 \\
    1 & Breadboard & 1, 2, 3 \\
    1 & Breadboard power supply & 1, 2, 3 \\
    1 & USB power supply cable & 1, 2, 3 \\
    1 & Jumper wire set & 1, 2 \\
    2 & Multimeters & 1, 2 \\
    1 & Mini screwdriver for multimeters & 1,2 \\
    5 & \SI{500}{mA} fusses for multimeters & 1,2 \\
    4 & Alligator clip leads & 1, 2 \\
    1 & \SI{1}{\mega\ohm} resistor & 2 \\
    2 & \SI{100}{\micro\farad} capacitor & 2 \\
    1 & \SI{5}{V}, \SI{650}{nm} laser module & 3 \\
    1 & Tape measure with cm scale & 3 \\            
    \hline\hline
  \end{tabular}
\end{table}

\section{Conclusion}
\textcolor{blue}{SFW and MWS write this together.}

We did it, and you can too!  We should have a resources page/EPAPS for this paper.

\begin{acknowledgments}
  Redacted for review.% This work has been supported by the NSF (Award \# 1725655).
\end{acknowledgments}

>>>>

\author{First Author} \affiliation{Masked Institution}

\author{Second Author} \affiliation{Masked Institution}

@@

% There is no abstract in a TPT paper.
% \begin{abstract}
%   A key problem facing physics departments, especially given the current global pandemic, is
%   how can we engage students in our laboratory courses while maintaining appropriate social
%   distancing and hygiene standards.  One solution to this problem is to move the labs to an
%   online format.  But how can we do this while \textit{also} engaging our students in online
%   labs with a curriculum that privileges science practices?  We have created an intro physics
%   lab curriculum that engages students in science practices and are implementing it online.
% \end{abstract}

@@

\section{Introduction}
There are many challenges that physics faculty face when teaching introductory labs. One of
these challenges is engaging students in authentic science practices.  Another has been
highlighted given the current global pandemic---specifically how to engage students in our
laboratory courses while maintaining appropriate social distancing and hygiene standards. We
have chosen to answer these challenges by transforming our labs\ldots\ twice. We discuss the
rationale behind the first transformation to a practice-focused curriculum.  When March 2020
rolled around we needed to transform our labs again, this time to accommodate online
learning. This paper discusses two chief questions: ``What are we doing to engage students in
science practices?'' and ``How did we make all of this work online?''

% Scientific truth is discovered through the practice of doing science.  \citeauthor{DBERreport}
% state, ``Without [scientific] investigative practices, there would be no new scientific and
% engineering knowledge.''\citep{DBERreport} Too often, our laboratory courses do not
% meaningfully engage students in scientific practices, instead reproducing classical
% experiments.\citep{PCAST12} This is part of a long-standing tradition of calling for authentic
% engagement in scientific practices which pre-dates Lorentz transformations.\citep{AAAS1881}
% Indeed, back in \citeyear{AAAS1881}, the AAAS stated our goals quite succinctly, ``[Typical
% courses in t]he sciences\ldots are not made the means of cultivating the observing powers,
% stimulating inquiry, exercising the judgment in weighing evidence, nor of forming independent
% habits of thought.''\citep{AAAS1881}

The physics labs at our institution in Fall 2016 very much mirrored the national narrative.
The lab curriculum had been largely unchanged for about 20 years. Moreover, the equipment
commonly used by students was outdated---triple beam balances and hand-drawn graphs were
standard.  In the same year, as part of an interdisciplinary team interested in engaging
students in scientific practices as well as assessing those scientific practices, we secured
funding, both internally and from the NSF, to change this status quo in physics, biology, and
chemistry.  All three departments transformed their labs using a pedagogical framework
entitled, Argument Driven Inquiry (ADI),\citep{Sampson2011,Walker2011,Walker2016} which has
been specifically designed to engage students in authentic science practices. In physics, we
also utilized the AAPT Lab Recommendations to guide our transformation.\citep{kozminski2014aapt}

We were satisfied with our progress when March 2020 rolled around, and with it, the mandatory
shut-down due to the global COVID-19 pandemic.  With students off campus, we had to abruptly
shift our delivery to an online format and quickly realized that some of the activities that we
utilized in the face-to-face sections had to be adapted to online use.  Going forward, we have
further adapted what we are doing so that students can still participate in a hands-on
laboratory experience in an online laboratory course.

\section{Instructional Context}

Regional State University is a public doctoral granting university in a rural, economically
depressed part of our state.  The university mission is focused on regional transformation and
service to this region.  The total combined student population in Fall 2019 was 28,651 largely
comprised of undergraduates (23,081). Our physics labs (Physics \textrm{I} lab and Physics
\textrm{II} lab) are each 1 credit courses that meet for 2 hours per week. These courses serve
both of our Calculus-based and Algebra-based physics lecture courses.  Most $(\sim 75\%)$ of
the students who take our lab course are in (or have taken) the corresponding Algebra-based
physics lecture course. These labs also fulfill the general education requirement for science
lab courses at our university.

Labs are supervised by Author 2, but each section is run by Graduate GTAs (GTAs). The
transformed curriculum was jointly written by both of the authors.  GTA training was also greatly
enhanced when the new lab curriculum was put in place.  Both authors, along with colleagues in
Biology and Chemistry, run a training for all GTAs in Biology, Chemistry, Geology, and Physics
as these disciplines are all using the same curricular format for their labs.  Author 2 runs a
weekly prep meeting with the GTAs, and Author 1 and the research team have supervised various
aspects of the transformation especially important for research such as curricular
implementation \citep{SmithJoyner2020} and assessment grading practices \citep{Wolf2019}.

\section{Transformation \#1: Argument Driven Inquiry}
Argument Driven Inquiry (ADI) is a pedagogical method that was developed to make science labs
in school better match what actually transpires in authentic research settings
\citep{Walker2011,Sampson2011,Walker2016}.  In traditional labs, we often ask students to
answer questions, or measure quantities, that are well-known using procedures that have been
refined over time.  In ADI labs, we give students a guiding question to answer experimentally
(e.g., ``Does the force a fan exerts on a cart depend on the mass of the cart?''). This allows
students to design a procedure for an experiment that will answer that question, collect and
analyze their data, and make claims based on their data.  We accomplish this by having students
engage in a three-part cycle:
\begin{itemize}
  \item Pre-Lab - Introducing the context
  \item Proposal Development and Data Collection
  \item Argumentation and Peer Review
\end{itemize}
In the sections below, we will comment on each part of the cycle, focusing on both students and
GTAs. Each lab course completes at least three cycles (usually four in the Fall and Spring),
and the semester ends with a practical exam where students engage in this process on a
shortened cycle without peer feedback.\cite{Wolf2019} We have provided supplemental materials
with more details about each of the labs in our curriculum.

\subsection{Session 1: Pre-Lab}
Part of the goal of any laboratory is to help students develop a familiarity with certain tools
and equipment common to the lab.  The purpose of the pre-lab reading and activity is to give
students familiarity with the equipment they will be using.  For the investigation described
previously, ``Does the force a fan exerts on a cart depend on the mass of the cart?''  we need
students to become familiar with a few things, such as what we mean by a cart, and give them
some tools that they need to be able to answer this question.  As a part of the pre-lab
reading, students are given information about linear regression---both how to run it in Excel,
and how to interpret the output, and how we can estimate instantaneous velocity given position
vs.\ time data. For this experiment, we give them a cart (leaving the fan off for now) and have
them measure the acceleration of that cart down a ramp using an ultrasonic motion detector to
collect position vs.\ time data for this motion.  Students work in pairs and turn in a brief
summary of this work on the course management system.  For this investigation, it is the first
time that they create graphs, so we set norms for graphing such as helping them decide which
variable to put on the x-axis and the y-axis as well as including units.  Pre-lab assignments
are designed to be graded in less than 1 minute/paper based on a rubric we provide to both
students and GTAs.

\subsection{Session 2: Proposal Development and Data Collection}
During this session, students work in groups of 3-4 on the guiding question.  They develop a
proposal, get it approved by a GTA, and then collect and analyze their data.  We have a format
for proposal development that asks students to link the scientific concept being studied---in
this example case, Newton's Second Law---to the data that they will collect.  Students also
need to propose a plan for analyzing their data and minimizing potential sources of error (such
as friction).  Once students have an approved proposal, they begin collecting and analyzing
their data.  This may lead them to refine or revise their method (which they are encouraged to
do).  Grading for the GTAs this week is minimal (students get full credit for getting their
proposal approved).  However, this is the most critical week for GTA training.  GTAs have to be
clear that the goal is to allow a diverse number of ways of collecting/analyzing this
data. This can be uncomfortable for the GTAs and students alike.  Students want ``the answer,''
and GTAs want to provide one to them.  However, experimental methods certainly have an impact
on experimental results. One of the goals of this curriculum is to get students to understand
this and apply it as they develop their experimental procedures and evaluate their results.

\subsection{Session 3: Argumentation and Peer Review}
During this session, the students begin by sharing their results.  Students finish analyzing
their data during the prior week, and prepare a ``poster'' on a whiteboard.  One person from
the group stays at the whiteboard while the other group members (travelers) go to other groups.
The travelers learn what other groups did, and compare to their results in a structured
argumentation setting.  Groups spend about 3--5 minutes at a poster, and rotate so that they
see at least 3 other posters.  After the travelers return, critically, the groups spend time
discussing what they saw and reflecting on their own results.  What is exciting is that
sometimes, these interactions actually drive groups to change their claims.\citep{Walker2019}

Each student writes a shortened lab report consisting of three sections: an introduction to the
scientific concept, a description of the experimental method or procedure, and a discussion
section laying out their results and the evidence and justification supporting their results.
The authors have created different peer review calibration videos for the students to watch so
they can look for the same things that we are going to be grading them on when we get their
final reports.  Students complete their lab report and submit it by the end of the day.  Then,
students take part in double-confidential peer review that we facilitate online.  They read and
review two different lab reports using the same rubric as we do on their final drafts.
Finally, they get their feedback and use this to revise their own lab report.  At the end of
this week, students turn in their revised, peer-reviewed final lab report.  This is the
heaviest week of GTA grading, each lab report generally takes about 3-5 minutes to grade.

@@

In March 2020 the COVID-19 pandemic forced most universities, including ours, to move all their
classes online. Our Physics \textrm{I} and \textrm{II} laboratories had completed two out of
four full investigations and the pre-lab for the third investigation face-to-face. We were
forced to find a way to engage students in an online format while preserving the nature of the
ADI laboratory experience. In addition, we gave the laboratory practical exam online. We
required student investigation groups to find a method for online collaboration in which
everyone in the group could participate. Tools students used were the Course Management System
communication tools (Canvas), WebEx (video interaction platform licensed by our university),
and other online communication applications not managed by the university (e.g., group
chats). We have detailed the adaptations we made to the curriculum in the supplementary
materials.  One of the principles that we used while making these adaptations is that students
should exclusively use university-supported (Microsoft Office) or open source resources.

The pre-lab phase was managed one of two ways.  As this is the most prescriptive part of the lab
and intended to introduce students to data collection and analysis techniques, in-person
activities were modified for online use by creating (or using) videos or simulated using
\emph{Glowscript}.\citep{glowscript} Students could collaborate with a partner asynchronously
for this part of the project.

Proposal development also occurred online asynchronously.  Each group produced their proposal
and posted a proposal form on a discussion board for approval. The GTA reviewed proposals and
provided feedback or approval. Groups used the GTA feedback to revise their proposals until
they were approved. Most proposals obtained approval after two or three revisions, but some
required as many as seven revisions to obtain approval. When the GTA approved a group's
proposal, they assigned the group a data set for the investigation, and the group began its
measurements and analysis. Based on our prior experience running the class, we prepared some
data sets appropriate to the different proposals that previous students had produced and
provided measurements to the current students in the most raw form possible to require them to
make decisions about data collection and analysis.

The argumentation session was held in a scheduled Cisco WebEx session during the lab session
the week after the proposal session. Before this session, each group was required to complete
its analysis and create a three-slide presentation for the argumentation session. The first
slide was a description of their measurements. The second slide was a presentation of the
results, including a graph or table, and the third slide was their argument, based on their
result.  One member of each group gave the presentation, which was followed by
questions. Students received credit for giving presentations, asking meaningful questions, and
responding to questions.  Following the argumentation session students submitted individual
draft reports, peer-reviewed each other's drafts, and submitted final reports in the same
manner used for the face-to-face investigations.

@@

@@

Early on, we decided to hold our introductory physics laboratory courses online in the Fall
2020 semester in order to preserve the group class interaction aspects of ADI, which would be
difficult under the social distancing requirements in place due to the
pandemic.\citep{mclber20} Learning from some of the challenges we faced in the Spring, we
informed the students before the course began that internet connectivity was required and that
they must have access to a computer capable of running \emph{Tracker}\citep{bro2009} and \emph{ImageJ}.\citep{schrasetal12} We also included these statements in the course
syllabus. Although we began the semester with the university open for socially distant
face-to-face learning, that has since ended and we have pivoted to online instruction only for
our undergraduate students.

Furthermore, so that we could provide students with a hands-on experience, we developed lab
kits with supplies that allowed the students to perform the investigations outside the teaching
laboratory. We purchased the lab kit items in collaboration with our campus bookstore, and the
students purchased the lab kits from the bookstore. We ordered lab kit items in bulk and where
possible directly from manufacturers to reduce the costs of the items. Each General Physics
Laboratory I kit costs \textcolor{red}{$\sim$}\$25.00, and each General Physics Laboratory II
kit costs \$39.00. And we have students paying for these kits in place of a physical lab
manual, which we provide online for this course.  The online adaptation of the face-to-face ADI
curriculum has remained unchanged --- pre-labs are done in small groups asynchronously,
proposals are developed in larger groups asynchronously, and argumentation sessions are
scheduled and occur via WebEx.

\section{Discussion}
We have observed a great number of successes for these transformations.  First and foremost, is
that we indeed have a lab curriculum that is aligned with national goals and
standards. Furthermore, we have successfully deployed this online with both short and longer
planning times.  Students are indeed engaging with science practices as determined by our
practical assessments, and our department culture around laboratory course instruction is
invigorated. Psychometric assessment of our students engagement with science practices is
ongoing.

The transition to online learning has not gone without hiccups.  Technology and access are two
key factors for success in online learning environments, which were a barrier for many of our
students.  Indeed our institution's center for survey research has published some findings that
explain some of our observed issues.\citep{ECUcovidSurvey} The GTAs and students found
communication about proposals much more difficult online than in face-to-face classes.  Indeed,
about 10-20\% of our students did not have reliable internet access after the transition to
online learning in the spring.\citep{ECUcovidSurvey} Also, up to 8\% of students did not have
access to a computer once they left campus.\citep{ECUcovidSurvey} Additionally, we noticed that
some students in the course did not have access to computers capable of running \emph{Tracker}
or \emph{ImageJ}, both of which run on Windows, Macintosh, or Linux computers but not
Chromebooks or mobile devices. We discovered \emph{jsTrack}\citep{jstrack}, an online
Javascript web application for video analysis that runs on most computers including
Chromebooks, but not mobile devices.

Many students could not or did not attend the online WebEx sessions or participate with their
assigned groups.  Once they left campus, many students found they had increased work or school
responsibilities (42.1\%) or additional family responsibilities (59.0\%).\citep{ECUcovidSurvey}
We removed non-participating students from groups and gave them an opportunity to make up their
missed work asynchronously. Less than \SI{50}{\percent} of the students in the make-up groups
completed their work.

Finally, we hope these changes will be meaningful long-term as a lack of online labs is also a
barrier for distance education students' completion of a degree.  So online lab curricula would
fill an institutional need.

\begin{acknowledgments}
  Redacted for review.% This work has been supported by the NSF (Award \# 1725655). We would
                      % also like to thank the Physics GTAs who have helped us develop
                      % resources and tutorials for students during this transition.
\end{acknowledgments}
